Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-07-20 manuscripts/manuscript1.qmd
something

library(targets)
library(tidyverse)
library(withr)
library(here)
library(formattable)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(flextable)

@@

>>>>

library(targets)
library(tidyverse)
library(withr)
library(here)
library(formattable)
library(janitor)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(flextable)

@@

There
